Exploring Local Explanations of Nonlinear Models Using Animated Linear Projections

### 2022-05-11 _paper.tex
extra comma removed
milk/dark classification title

\hypertarget{chocolates-milkdark-chocolate-classification}{%
\subsection{Chocolates, Milk/Dark Chocolate Classification}\label{chocolates-milkdark-chocolate-classification}}

@@

Figure \ref{fig:casefifa}, tests the support of the local explanation. Offensive and reaction skills (\texttt{off} and \texttt{rct}) are both crucial to explaining a star offensive player. If either of them were rotated out, the other would be rotated into the frame, maintaining a far-right position. However, increasing the contribution of a variable with low importance would rotate both features out of the frame.

>>>>

\hypertarget{chocolates-milkdark-classification}{%
\subsection{Chocolates, Milk/Dark Classification}\label{chocolates-milkdark-classification}}

@@

Figure \ref{fig:casefifa} tests the support of the local explanation. Offensive and reaction skills (\texttt{off} and \texttt{rct}) are both crucial to explaining a star offensive player. If either of them were rotated out, the other would be rotated into the frame, maintaining a far-right position. However, increasing the contribution of a variable with low importance would rotate both features out of the frame.
